Sampling requirements to detect ecosystem change

### 2020-01-04 R/manuscript_draft.Rmd
minor text changes

One of the primary goals of monitoring programs is to detect long-term ecological change.

@@

- Here, we develop a set of tools to determine the appropriate number of samples and sampling approach when dealing with data sources where additional samples can be added. We first investigate these tools using a simulated-based apporach. We then apply these tools to the detection of change points for a set of lakes...

>>>>

One of the primary goals of monitoring programs is to detect long-term ecological change...

@@

Here, we develop a set of tools to determine the appropriate number of samples and sampling approach when dealing with data sources where additional samples can be added. We first investigate these tools using a simulated-based apporach. We then apply these tools to the detection of change points for a set of lakes...
